Coherent optical association of a single molecule

### 2020-09-20 paper.tex
whitespace, regenerate PDF
Update on Overleaf.

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using an optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state. Our scheme is based on theoretically determined most suitable vibrational state of the electronic excited state $c^3\Sigma^+$ that balances transfer coupling and photon scattering. Furthermore, to reduce technical requirements such as intensity stability, etc , we choose a initial and final state ... This approach is general and can be use to associate other molecular species or large molecules atom-by-atom.
%electronic the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering. Using these parameters, we demonstrate coherent association of a electronic ground-state molecule from two atoms via an optical Raman transition in an optical tweezer.

@@

While optical Raman transfer of atoms to molecules utilizing an electronic excited state has been shown previously\todo{cite}. Those demonstrations were  incoherent  where the signal comes from loss of population (and therefore more like spectroscopy and the transferred molecules cannot be further utilized). The challenge lies at  achieve high enough Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state.
 Previous experiments use weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency. However, this choice of state also increases the scattering during the transfer process for two reasons.
Firstly, since for a typical molecular potential the spacing between states
decreases with increasing vibrational levels,
a weakly bound excited molecular state limits maximum usable detuning and therefore the effectiveness of scattering reduction by increasing the detuning for the Raman transition.
Secondly, due to size similarity, the weakly bound molecular ground state has a strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
The rate of such scattering process is proportional to $1/\delta_{thresh}^2$,
where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
% This further increases the scattering rate for a weakly bond excited state.
Based on these considerations, we calculated both the Raman Rabi frequency and the scattering rate at different detunings. As seen in figure (1....), despite a higher Raman Rabi frequency at the same detuning, using a weakly bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states. As a result, we use a deeply bound molecular excited state to drive the Raman transition.

>>>>

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using an optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state. Our scheme is based on a theoretically determined  vibrational state of the electronic excited state $c^3\Sigma^+$ that has the best transfer Rabi coupling to photon scattering ratio. Furthermore, to reduce technical requirements such as intensity stability, etc , we choose a initial and final state ... The choice of the states is general and can be applied to associate other molecular species or large molecules atom-by-atom.
%electronic the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering. Using these parameters, we demonstrate coherent association of a electronic ground-state molecule from two atoms via an optical Raman transition in an optical tweezer.

@@

While optical Raman transfer of atoms to molecules utilizing an electronic excited state has been shown previously\todo{cite}. Those demonstrations were  incoherent  where the signal comes from loss of population (and therefore more like spectroscopy and the transferred molecules cannot be further utilized). The challenge lies at  achieve high enough Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state.
 Previous experiments use weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency. However, this choice of state also increases the scattering during the transfer process for two reasons.
Firstly, since for a typical molecular potential the spacing between states
decreases with increasing vibrational levels,
a weakly bound excited molecular state limits maximum usable detuning and therefore the effectiveness of scattering reduction by increasing the detuning for the Raman transition.
Secondly, due to size similarity, the weakly bound molecular ground state has a strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
The rate of such scattering process is proportional to $1/\delta_{thresh}^2$,
where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
% This further increases the scattering rate for a weakly bond excited state.
Based on these considerations, we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in figure (1....), despite a higher Raman Rabi frequency at the same detuning, using a weakly bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states. As a result, we use a deeply bound molecular excited state to drive the Raman transition. (mention the trend, also v=12 will work as similarly as v=0)
